---
title: "Function Details"
bibliography: [../../inst/REFERENCES.bib]
biblio-style: apalike
link-citations: yes
#nocite: | 
#  @Gamma1995
#  @Fowler2002
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

<!-- One line about what the function does -->

Mediates between the domain and data mapping layers using a collection-like
interface for accessing domain objects.

<!-- Introduction Visual -->

<!-- Introduction Text -->

## How It Works

text

## When to Use It

text

## Example: Name of Example 1

text

## Example: Name of Example 2

text

## Workflow:

1.  Optional: Call `ddd::use_ddd` maximum once per project; this will make the
    project independent of `ddd`
2.  Call `ddd::add_entity` with its respective arguments
3.  Call `devtools::document` (or Ctrl+Shift+D on windows) to include the Entity
    in the project NAMESPACE file
4.  Call `devtools::test` (or Ctrl+Shift+T on windows) to validate that the
    Entity's unit-test pass

## Further Reading

```{r, message=TRUE}
message("Signifies a tip or suggestion")
```

```{r, warning=TRUE}
warning("Signifies a general note")
```

```{r, error=TRUE}
stop("Signifies a warning or caution")
```
