---
title: "Value Object"
bibliography: [../references.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
path <- tempfile("docs-")
dir.create(path, F, T)
```

## What is a Value Object?

In the context of DDD, a ***Value Object*** models a domain concept. A **Value
Object** is an object that is identified only by its data and doesn't have a
long-lived identity.

For example, think about the diners, i.e. customers, of a Pizzeria. Associating
an order and a client requires ephemeral customer identity. The customer name
matters. It is used to identify for whom a particular Pizza was made. The names
Hilary and Bill are not equal. However, once the customer leaves the Pizzeria,
the customer's existence dissipates. On the other hand, if the customer is
enrolled in a restaurant loyalty program, then its unique identifier on the
system is both essential and long-lived.

<!-- ## Description -->

<!-- When you care only about the attributes of an element of the model, classify it -->

<!-- as a **Value Object**. Make it express the meaning of the attributes it conveys -->

<!-- and give it related functionality. Treat the **Value Object** as immutable. -->

<!-- Don't give it any identity and avoid the design complexities necessary to -->

<!-- maintain **Entities**. [@Evans2004, p. 99] -->

<!-- ## Highlights -->

<!-- -   Calling a Value Object without any input arguments returns the Null Value -->

<!--     Object, which is usually an empty data.frame with column names and classes. -->

<!-- -   Equating Value Objects is based on field-based implementation, rather than -->

<!--     identity based implementation. That means, two records are equal if all -->

<!--     their fields are equal. -->

<!-- -   Value Objects can receive other Value Objects. -->

<!-- -   Value Objects can receive one or a set of Entities. -->

## What does `add_value_object` do?

Given the **Value Object** name (Customer), and the sub-domain name (pizza
ordering),

When `add_value_object` is called

```{r, eval = FALSE, echo = TRUE}
add_value_object(name = "Customer", domain = "pizza ordering")
```

```{r, eval = TRUE, echo = FALSE}
name = "Customer"; domain = "pizza ordering"
withr::with_dir(path, add_value_object(name, domain))
file_path <- list.files(path, filename$value(name, domain), recursive = TRUE)
```

Then the function:

-   Creates a **Value Object** boilerplate with several input arguments;
-   Places the file at `r file_path`; and
-   Opens the file (only in interactive mode).

The boilerplate code produced by `add_value_object` looks likes this:

```{r code = readLines(fs::path(path, file_path)), eval=FALSE, echo=TRUE}
```

## Why should I use Value Objects in my design?

The simplest way to implement a **Value Object** in R is with a function that
returns a data.frame row. Compare the following two patterns for creating a
data.frame that holds a Customer data.

First, using the `tibble::tibble` function directly for constructing the
Customer

```{r, eval=FALSE, echo=TRUE}
customer <- tibble::tibble(given = "Bilbo", family = "Baggins")
```

Second, using a **Value Object** as a surrogate for constructing the Customer

```{r, eval=FALSE, echo=TRUE}
Customer <- function(given = NA_character_, family = NA_character_){
    stopifnot(is.character(given))
    stopifnot(is.character(family))
    tibble::tibble(given = given, family = family)
}

customer <- Customer(given = "Bilbo", family = "Baggins")
```

Both patterns return identical objects, equal in content and structure i.e.
column names and classes.

Why would one prefer using a **Value Object** over the direct alternative? There
are three apparent qualities offered by the **Value Object** pattern which are
not offered by the alternative:

-   Safety. Each input argument belongs to a certain class. This is guaranteed
    by type checking at the beginning of the function.

-   NULL **Value Object**. Calling the **Value Object** with no input arguments
    returns the structure of the `tibble` with default content, such as `NULL`,
    `NA`, or actual values.

-   Default values for missing input arguments. In this manner, the **Value
    Object** has a well-defined behaviour for a customer without a last name,
    such as Madonna and Bono.

## References
