---
title: "Introduction to Domain-driven Design (ddd)"
bibliography: []
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

## Conventions Used in this Package Documentation

The following typographical conventions are used in this package documentation:

-   ***strong italic***: indicates new terms;

-   **bold**: indicates package & file names;

-   `inline code:` mono-spaced highlighted text indicates functions or other
    commands that could be typed literally by the user; and

-   code chunk: indicates commands or other text that could be typed literally
    by the user.

    ```{}
    1+2
    ## [1] 3
    ```

In addition to the general text used throughout, you will notice the following

<!-- code chunks with images: -->

```{r, message=TRUE}
message("Signifies a tip or suggestion")
```

```{r, warning=TRUE}
warning("Signifies a general note")
```

```{r, error=TRUE}
stop("Signifies a warning or caution")
```
