---
title: "Step 1: Create a Series of Domain Events"
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

## Conceptual Level

The first step of modelling a domain is thinking about what are the activities that domain experts care about.

What activities do experts from the Pizza ordering domain care about? Think like a pizzeria employee at the counter. How does the business process - ordering a pizza - look like?

```{r domain-event-table}
ddd::event_storming %>% 
    dplyr::transmute(Event = title$event(Event), Example = title$exammple(Example)) %>% 
    tibble::rowid_to_column("#") %>% 
    kable(caption = "Pizza-Ordering Event Table")
```

## Implementation Level

We can add these domain events to our application by using `add_domain_event()`. The function takes two arguments:

(1) `name` - domain event name; and
(2) `domain` - the domain name.

```{r domain-event-code}
domain_event_snippet <- 
    ddd::event_storming %>% 
    dplyr::mutate(Event = title$event(Event)) %>% 
    dplyr::distinct(Event) %>% 
    tibble::add_column(Domain = title$domain("pizza ordering")) %>% 
    stringr::str_glue_data('add_domain_event(name = "{Event}", domain = "{Domain}")')
```

```{r code=domain_event_snippet, eval=FALSE, echo=TRUE}
```
