---
title: "Step 1: Create a Series of Domain Events"
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

The first step of modelling a domain is thinking about what are the activities
that domain experts care about.

What activities do experts from the Pizza ordering domain care about? Think like
a pizzeria employee at the counter. How does the business process - ordering a
pizza - look like?


```{r domain-event-table}
cache$load("event_storming") %>% 
    dplyr::select(Event, Example) %>% 
    tibble::rowid_to_column("#") %>% 
    kable(caption = "Pizza-Ordering Event Table")
```

We can add these domain events to our application by using `add_domain_event()`.
The function takes two arguments:

(1) `name` - domain event name; and 
(2) `domain` - the domain name.

```{r domain-event-code}
domain_event_snippet <- 
    cache$load("event_storming") %>% 
    dplyr::mutate(Event = to_snake_case(Event)) %>% 
    dplyr::distinct(Event) %>% 
    stringr::str_glue_data('add_domain_event("{Event}", domain = "pizza_ordering")')
```

```{r code=domain_event_snippet, eval=FALSE, echo=TRUE}
```
