---
title: "Step 2: Create the Commands that cause each Domain Event"
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "R",  "_common.R"))
```

The first step of modelling a domain is thinking about what are the activities
that domain experts care about.

What activities do experts from the Pizza ordering domain care about? Think like
a pizzeria employee at the counter. How does the business process - ordering a
pizza - look like?



1. *Order issued*
1. *Pizza added to order*
1. *Pizza size decided* (say, medium) 
1. *Topping added* (say, olives)
1. *Topping added* (say, anchovy but only on the right half)
1. *Topping removed* (say, no olives)
1. *Pizza reviewed*
1. *Order confirmed*



We can add these domain events to our application by using `add_domain_event()`.
The function takes two arguments (1) `name` - domain event name; and (2)
`domain` - the domain name.

```{r code=readLines(system.file("inst", "snippets", "pizza-domain-events.R")), eval=FALSE, echo=TRUE}
```
