---
title: "Add a Value Object to a Domain"
bibliography: [references.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
path <- tempfile("docs-")
dir.create(path, F, T)
```

## What is a Value Object?

A ***Value Object*** is a function that receives input, applies some
transformations, and outputs the results in some data sturicture such as a
`vector`, a `list` or a `data.frame`.

```{=html}
<div class="alert alert-info" <strong="">
In R, a good practice is to set the Value Object to return a `data.frame` at its
output. This is because often the Value Object is called during data
wrangling operations.
</div>
```

A light example of a **Value Object** is one that receives a character vector,
applies the `identity` function, and organises the character vector in a
`data.frame`.

```{r, eval=TRUE, echo=TRUE}
Alphabet <- function(letters = LETTERS){
  stopifnot(is.character(letters)) # Value Object type check
  letters <- identity(letters)     # Value Object transformation
  data.frame(letter = letters)     # Value Object return object
}

head(Alphabet())
```

In the context of DDD, a ***Value Object*** models a domain concept. A **Value
Object** is an object that is identified only by its data and doesn't have a
long-lived identity.

For example, think about the diners, i.e. customers, of a Pizzeria. Associating
an order and a customer requires ephemeral customer identity. The customer name
matters. It is used to identify for whom a particular Pizza was made for. The
names Hilary and Bill are not equal. However, once the customer leaves the
Pizzeria, the customer's existence dissipates. On the other hand, if the
customer is enrolled in a restaurant loyalty program, then its unique identifier
on the system is both essential and long-lived.

## What does `add_value_object` do?

Given the **Value Object** name \<Customer\>, and its sub-domain name \<pizza
ordering\>,

When `add_value_object` is called

```{r, eval = FALSE, echo = TRUE}
add_value_object(name = "Customer", domain = "pizza ordering")
```

```{r, eval = TRUE, echo = FALSE}
name = "Customer"; domain = "pizza ordering"
withr::with_dir(path, add_value_object(name, domain))
file_path <- list.files(path, filename$value(name, domain), recursive = TRUE)
```

Then the function:

-   Creates a **Value Object** boilerplate with several input arguments;
-   Places the file at `R/pizza_ordering-value-Customer.R`; and
-   Opens the file (only in interactive mode).

## What are the main components of a Value Object?

The boilerplate code produced by `add_value_object` looks likes this:

```{r code = readLines(fs::path(path, file_path)), eval=FALSE, echo=TRUE}
```

The boilerplate code includes three key activities covered by any **Value
Object**:

-   Assigning default values to input argument values, such as different types
    of NA.
-   Validating the type and value range (if applicable) of the input arguments;
    and
-   Organizing the input arguments in a data structure, such as a `data.frame`.

In addition, the **Value Object** include transformations on the input arguments
before enframing them in a data structure. Common transformations include:
`base::serialize`, `jsonlite::toJSON`, `tidyr::unite`, and
`snakecase::to_title_case` to name a few.

## Why should I use Value Objects in my design?

The simplest way to implement a **Value Object** in R is with a function that
returns a data.frame row. Compare the following two patterns for creating a
data.frame that holds a Customer data.

First, using the `tibble::tibble` function directly for constructing the
Customer

```{r, eval=FALSE, echo=TRUE}
customer <- tibble(given = "Bilbo", family = "Baggins")
```

Second, using a **Value Object** as a surrogate for constructing the Customer

```{r, eval=FALSE, echo=TRUE}
Customer <- function(given = NA_character_, family = NA_character_)
{
    stopifnot(is.character(given))
    stopifnot(is.character(family))
    tibble(given = given, family = family)
}

customer <- Customer(given = "Bilbo", family = "Baggins")
```

Both patterns return identical objects, equal in content and structure i.e.
column names and classes.

Why would one prefer using a **Value Object** over the direct alternative? There
are three apparent qualities offered by the **Value Object** pattern which are
not offered by the alternative:

-   Safety. Each input argument belongs to a certain type. This is guaranteed by
    type checking at the beginning of the function.

-   NULL **Value Object**. Calling the **Value Object** with no input arguments
    returns the structure of the `tibble` with default content, such as `NULL`,
    `NA`, or actual values.

-   Default values for missing input arguments. In this manner, the **Value
    Object** has a well-defined behaviour for a customer without a last name,
    such as Madonna and Bono.

There are more subtle qualities offered by a **Value Object** over direct
implementation. First, it allows you to capture new knowledge about the domain.
Say, you have discovered that the Pizzeria makes deliveries. In this case, the
Customer details need to include an address and a phone number. With a **Value
Object**, you can rewrite the Customer concept as:

```{r, eval=FALSE, echo=TRUE}
Customer <- function(given = NA_character_, family = NA_character_, 
                     phone = NA_integer_, address = NA_character_)
{
    stopifnot(is.character(given))
    stopifnot(is.character(family))
    stopifnot(is.integer(phone))
    stopifnot(is.character(address))
    tibble(given = given, family = family, phone = phone, address = address)
}
```

Notice that former calls to `Customer` in the code base, which modelled the
ordering pizza process for diners, are not impacted by the added input
arguments. For example, the call of previous diner works well.

```{r, eval=FALSE, echo=TRUE}
customer <- Customer(given = "Bilbo", family = "Baggins")
```

The **Value Object** ascribes NA values for the phone number and address of
diners, that is customers in the restaurant.

The second subtle quality regards tests. With **Value Object** you can replace
Without a **Value Object**, your test expectations capture only the available
knowledge at the moment of writing the test. For example, a test that validates
the structure of a returning data from a function call,

```{r, eval=FALSE, echo=TRUE}
test_that('calling Order$get_customer_info() returns the desired results', {
    expect_setequal(
        colnames(Order$get_customer_info()),
        c("given", "family", "phone", "address")
    )
})
```

can instead be written against the `Customer` **Value Object**,

```{r, eval=FALSE, echo=TRUE}
test_that('calling Order$get_customer_info() returns the desired results', {
    expect_setequal(
        colnames(Order$get_customer_info()),
        colnames(Customer())
    )
})
```

By avoiding hard coding of column names, your tests evolve along side the code
base.

## How Should I use Value Objects in my design?

1.  Querying an **Entity** , that is by using its public query methods, should
    return a **Value Object**.

2.  Calling **Value Object** can happen inside another **Value Object**.

3.  Reusing **Value Object** in tests, such as unit-tests and integration-tests,
    is useful when the test aims to capture the structure of a returning object.

The following example shows how to embed the `Customer` **Value Object** in the
pizza `Order` Entity

```{r, echo=TRUE, eval=FALSE}
Order$set("public", "set_customer_info", function(
  given = NA_character_, family = NA_character_){
  self$customer <- Customer(given, family)
  return(self)
})  
```

Then we can test the result of a call for this function

```{r, echo=TRUE, eval=FALSE}
test_that('calling Order$set_customer_info returns the customer info', {
    expect_setequal(
        colnames(Order$new(id = 1)$set_customer_info("Bilbo")$customer),
        colnames(Customer())
    )
})
```
