---
title: "Add an Entity to a Domain"
bibliography: [../references.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
name <- "Order"
domain <- "Pizza Ordering"
commands <- "Add Item to Order"
queries <- "Review Order"

path_proj <- tempfile("article-")
path_script <- file.path("R", filename$entity(name, domain))
path_test <- file.path("tests", "testthat", "test-" %+% filename$entity(name, domain))
fs::dir_create(path_proj)
```

## What does `add_entity` do?

Given the **Entity** `name`, and its `domain` name, and optionally `commands`
and `queries` methods,

When `add_entity` is called

```{r, eval = TRUE, echo = FALSE}
command <- "add_entity(name = '" %+% name %+% 
    "', domain = '" %+% domain %+% 
    "', commands = '" %+% commands %+% 
    "', queries = '" %+% queries %+%
    "')"
withr::with_dir(path_proj, eval(parse(text=command)))
```

```{r, code = command, eval = FALSE, echo = TRUE}
```

Then the function:

-   Generates boilerplate code for the **Entity** and saves it at **`r path_script`**; 
-   Generates a unit-test for the **Entity** and saves it at **`r path_test`**; and
-   Opens the files (only in interactive mode).

## What are the main components of an **Entity**?

The boilerplate code produced by `add_entity` looks likes this:

**`r path_script`**

```{r code = readLines(file.path(path_proj, path_script)), eval = FALSE, echo = TRUE}
```

**`r path_test`**

```{r code = readLines(file.path(path_proj, path_test)), eval = FALSE, echo = TRUE}
```


<!-- ## What is an Entity? -->

<!-- Entities are the first natural place we should aim to place business logic in -->
<!-- domain-driven applications. -->
