---
title: "Add an Entity to a Domain"
bibliography: [../references.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
name <- "Order"
domain <- "Pizza Ordering"
commands <- "add_item_to_order"
queries <- "review_order"

path_proj <- tempfile("article-")
path_script <- file.path("R", filename$entity(name, domain))
path_test <- file.path("tests", "testthat", "test-" %+% filename$entity(name, domain))
fs::dir_create(path_proj)
```

## What does `add_entity` do?

Given the **Entity** `name`, and its `domain` name, and optionally `commands`
and `queries` methods,

When `add_entity` is called

```{r, eval = TRUE, echo = FALSE}
command <- "add_entity(name = '" %+% name %+% 
    "', domain = '" %+% domain %+% 
    "', commands = '" %+% commands %+% 
    "', queries = '" %+% queries %+%
    "')"
withr::with_dir(path_proj, eval(parse(text=command)))
```

```{r, code = command, eval = FALSE, echo = TRUE}
```

Then the function:

-   Generates boilerplate code for the **Entity** and saves it at
    **`r path_script`**;
-   Generates a unit-test for the **Entity** and saves it at **`r path_test`**;
    and
-   Opens the files (only in interactive mode).

```{=html}
<div class="alert alert-info" <strong="">
You don't need to remember the naming style for the different DDD components.
Instead, <code>ddd</code> takes care of naming style for all domain objects. This way DDD file names, classes and functions are congruent with each other.
</div>
```
## What are the main components of an **Entity**?

The boilerplate code for the `r name` Entity class produced by `add_entity`
looks likes this:

**`r path_script`**

```{r code = readLines(file.path(path_proj, path_script)), eval = FALSE, echo = TRUE}
```

Notice the three public methods created by `add_entity`:

1.  `initialize` constructs a new object. By DDD definition, every entity must
    have a unique id (`uid`) which distinguishes it from other entities.
2.  `add_item_to_order`
3.  `review_order`

**`r path_test`**

```{r code = readLines(file.path(path_proj, path_test)), eval = FALSE, echo = TRUE}
```

<!-- ## What is an Entity? -->

<!-- Entities are the first natural place we should aim to place business logic in -->

<!-- domain-driven applications. -->
